Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-05-09 paper.tex
Updates following discussion with Soudabeh

The number of files selected for every subject is randomly selected in
a uniform distribution $U(\textit{a},\textit{b})$, where \textit{\textbf{b}} is set to the total
number of files $N_{f}$ and \textit{\textbf{a}} is set according to training ratio ($\alpha$) as follow:

\[
  \begin{cases}
          \textit{\textbf{a}} = 0      & \text{if $\alpha \leq 0.5$ }\\

          \textit{\textbf{a}} = (2\alpha - 1) N_{f} & \text{if $\alpha > 0.5$}
  \end{cases}
\]

@@

\paragraph{Random File Numbers (Triangular) -- RFNT}
The number of files selected for every subject is randomly selected in
a triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} 
and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the other 
two parameters could be set according to two different approaches. By considering $\alpha$ 
as training ratio, the distribution average equals to $\alpha N_{f}$ which that means 
for $\alpha$ less than $\nicefrac{1}{3}$ the lower limmit \textit{\textbf{a}} would 
get a negative value in this regard, therefore to avoid this issue the uniform distribution 
is applied for $\alpha < \nicefrac{1}{3}$. But for $\alpha \leq \nicefrac{1}{3}$ the following 
approaches are applicable. This distribution aims at sampling files produced towards 
the end of the pipeline execution.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adding biases}
In this part of the experiment, the effect of both subjects' and files' biases are considered in the predicted value. 
Our three random sampeling techniques are compered in Figure~\ref{fig:ALS-Bias-PFS} accross the accretion of training 
ratio;$\alpha$; and the results are reported at the following subsections.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of random methods in three different condition pairs with cosidering Bias of both subjects and files}
        \label{fig:ALS-Bias-PFS}
\end{figure}

\subsubsection{RFNU}
The obtained results show that by sampling at least half of the utility matrix, 
the predicted accuracy would be as accurate as the baseline (Random Unreal technique) 
but for the $\alpha$ of less than $50\%$ this is not true. Actually there is a 
difference range of $0.2$ to $0.7$ between the accuracy of Random Unreal and RFNU techniques for
$\alpha <0.5$ in C5C7 and C6C7 but this range chanhe to $(0.07,0.17)$ in C5C6.

\subsubsection{RFNT-L}
As it mentioned earlier RFNT-L technique is applicable for $\alpha \leq \nicefrac{1}{3}$, therefore its 
accuracy description is summerized for $\alpha > 0.3$. This accuracy of this technique is always higher than 
dummy classifier. Results show that this RFNT-L reaches to $100\%$ accuracy by $\alpha >0.8$ in condition pairs
with more errors, however the baseline never reached this high accuracy throughout of whole experiment.

\subsubsection{RFNT-S}
This sampling technique is as precise as Random Unreal with maximum difference gap of 0.07 between them which that 
happend in C5C7 at $\alpha = 0.7$ with accuracy of $0.91$.

>>>>

The number of files selected for every subject is randomly selected in
a uniform distribution $U(\textit{a},\textit{b})$, where \textit{b} is set to the total
number of files $N_{f}$ and \textit{a} is set according to training ratio $\alpha$ as follows:

\[
  \begin{cases}
          \textit{a} = 0      & \text{if $\alpha \leq 0.5$ }\\

          \textit{a} = (2\alpha - 1) N_{f} & \text{if $\alpha > 0.5$}
  \end{cases}
\]

@@

\paragraph{Random File Numbers (Triangular) -- RFNT}
The number of files selected for every subject is randomly selected in
a triangular distribution with parameters \textit{a}, \textit{b} and 
\textit{c} (\todo{see Figure X}) where \textit{b} is set to $N_{f}$ and the other two 
parameters can be set with two approaches meant to ensure that the 
average of the distribution is $\alpha N_{f}$ ($\alpha$ is the training 
ratio):
\begin{enumerate}
        \item Largest-a (RFNT-L): In this approach, a is set to the 
        largest possible value, i.e., b. The average of the 
        distribution is $\frac{a+N_{f}}{2}$, therefore, 
        a=$(2\alpha-1)N_{f}$.
\end{enumerate}

By considering $\alpha$ 
as training ratio, the distribution average equals to $\alpha N_{f}$ which that means 
for $\alpha$ less than $\nicefrac{1}{3}$ the lower limmit \textit{\textbf{a}} would 
get a negative value in this regard, therefore to avoid this issue the uniform distribution 
is applied for $\alpha < \nicefrac{1}{3}$. But for $\alpha \leq \nicefrac{1}{3}$ the following 
approaches are applicable. This distribution aims at sampling files produced towards 
the end of the pipeline execution.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{ALS with biases}
In this part of the experiment, the effect of both subject and file 
biases are considered in the prediction. Our three random sampling 
techniques (RFNU, RFNT-L and RFNT-S) are compared in 
Figure~\ref{fig:ALS-Bias-PFS} as a function of the training 
ratio $\alpha$.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of random methods for three different condition pairs (ALS with Bias).}
        \label{fig:ALS-Bias-PFS}
\end{figure}
\todo{Add $\alpha$ to the x labels in the Figure}

All three methods reach the accuracy of the baseline Random Unreal 
method from $\alpha$=0.5. RFNT methods reach this accuracy earlier than 
RFNU, from $\alpha$=0.4. For lower training ratios, all methods 
outperform the dummy classifier for one condition pair (CentOS5 vs 
CentOS6) but this is not the case for the other conditions. It should 
be noted that, as explained before, the three methods boil down to the 
same one (RFNU) for $\alpha<$0.3.
